Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-11 WSSSPE4_report/WSSSPE4_paper.tex
typo

\begin{abstract}
This report records and discusses the Fourth Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE4). The report
includes a description of the keynote presentation of the workshop, the
mission and vision statements that were drafted at the workshop and
finalized shortly after it, a set of idea papers, position papers, experience
papers, demos, and lightning talks, and a panel discussion.  The main part of the report
covers the set of working groups that formed during the meeting, along with contact information for readers who may want to join
the group. Finally, we present results from a survey of the workshop attendees.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Attendees}  \label{sec:attendees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%The following is a list of attendees at WSSSPE4.
%
%{\scriptsize
%\begin{longtable}{lll}
%\input{participants}
%\end{longtable}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Travel award recipients}  \label{sec:awardees}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}
%The following table contains the list of WSSSPE4 travel award recipients, where
%\textsuperscript{*} and \textsuperscript{\textdagger} indicate students and
%early-career researchers, respectively.
%
%{\scriptsize
%\begin{longtable}{lll}
%\input{awardees}
%\end{longtable}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Program committee}  \label{sec:progcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The WSSSPE4 program committee comprised:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Detailed survey results}  \label{sec:survey_details}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\input{survey_details}

%\input{wg_appendix_best_practices}

>>>>

\begin{abstract}
This report records and discusses the Fourth Workshop on Sustainable
Software for Science: Practice and Experiences (WSSSPE4). The report
includes a description of the keynote presentation of the workshop, the
mission and vision statements that were drafted at the workshop and
finalized shortly after it, a set of idea papers, position papers, experience
papers, demos, and lightning talks, and a panel discussion.  The main part of the report
covers the set of working groups that formed during the meeting, along with contact information for readers who may want to join
a group. Finally, we present results from a survey of the workshop attendees.

@@

The WSSSPE4 program committee comprised:

@@
